Make a README

### 2024-09-21 make_readme.qmd
Mention CFF
Published articles are mostly a matter of citation

:   What is the project about? What are its features? Is there a published article associated with it?

@@

:   Is there a recommended way to cite this project? We recommend to increase citability by using the [CodeMeta generator](https://codemeta.github.io/codemeta-generator/) to create a file called `codemeta.json`. Alternatively, one can also use the R package [`codemetar`](https://docs.ropensci.org/codemetar/) to create this file. Then, put it into the project folder.

@@

:   Under which license are the contents in this project available?

>>>>

:   What is the project about? What are its features? Why was it created?

@@

:   Is there a recommended way to cite this project? Is there a published article associated with it that you would like to have cited? We recommend to increase citability by using the [CodeMeta generator](https://codemeta.github.io/codemeta-generator/) to create a file called `codemeta.json`. Alternatively, one can also use the R package [`codemetar`](https://docs.ropensci.org/codemetar/) to create this file. Then, put it into the project folder. Another common standard is the [Citation File Format](https://citation-file-format.github.io/) (CFF), which is an equally valid option.

@@

:   Under which licenses are the works in this project available?
